---
title: "NC Electricity Demand Analysis"
author: "Erin Lee and Lexi Nelson"
date: "2026-04-23"
output:
  pdf_document:
    latex_engine: xelatex
---

## Executive Summary

Our project analyzes the relationship between temperature and electricity demand 
in North Carolina from 2000 to 2025. A visual is provided that highlights 
sectoral differences across residential, commercial, and industrial customers. 
The results of sensitivity analysis confirm our hypothesis that the residential 
sector is both the largest contributor to total demand and the primary source of 
volatility, exhibiting strong seasonal peaks driven by heating and cooling 
needs. Demand is shown to increase most sharply during extreme heat but also 
during cold conditions. Time series decomposition reveals that even as 
residential demand peaks have intensified, temperature variability itself has 
not significantly increased over time. This suggests that growing grid stress in 
North Carolina is driven more by changes in demand such as increased electric 
cooling than by changes in climate variability alone, highlighting the need for 
targeted demand-side management and energy efficiency policies.

## Introduction

In North Carolina, residential electricity demand, which is the largest and most 
variable component of the total electricity demand, is strongly influenced by 
temperature fluctuations that affect heating and cooling needs. Understanding 
the sectoral response to temperature changes is critical for ensuring grid 
reliability and informing future planning. This project examines monthly 
electricity demand from 2000 to 2025 across the residential, commercial, and 
industrial sectors. We integrate these data with average temperature, heating 
degree days (HDD), and cooling degree days (CDD) to explore the drivers of 
demand variability.
The analysis has three components. First, we show a baseline comparison 
of sectoral demand to highlight differences in scale and volatility across 
residential, commercial, and industrial electricity demand. Second, the 
sensitivity of each sector to temperature changes is demonstrated using both 
visual and statistical methods. Finally, long term trends are evaluated to 
determine whether increasing demand peaks are associated with rising temperature 
variability or structural changes in electricity use. By identifying drivers of 
demand fluctuations, this study provides insight into how North Carolina’s 
electricity system can improve grid resilience and meet peak demand moving 
forward.





```{r setup, include=FALSE}

library(tidyverse); library(lubridate)

# 1. Load temperature data
avg_temp <- read_csv("data_NC/AverageTemp.csv", skip = 2) %>% 
  rename(AvgTemp = Value)

max_temp <- read_csv("data_NC/MaxTemp.csv", skip = 2) %>% 
  rename(MaxTemp = Value)

min_temp <- read_csv("data_NC/MinTemp.csv", skip = 2) %>% 
  rename(MinTemp = Value)

cdd <- read_csv("data_NC/CoolingDegreeDays.csv", skip = 2) %>% 
  rename(CDD = Value)

hdd <- read_csv("data_NC/HeatingDegreeDays.csv", skip = 2) %>% 
  rename(HDD = Value)

# 2. Combine weather data and convert Date format
weather_data <- avg_temp %>%
  left_join(max_temp, by = "Date") %>%
  left_join(min_temp, by = "Date") %>%
  left_join(cdd, by = "Date") %>%
  left_join(hdd, by = "Date") %>%
  mutate(Date = ymd(paste0(Date, "01")))


# 3. Load electricity demand data
elec_demand <- read_csv("data_NC/ElectricityDemand.csv", 
                        skip = 8, col_names = FALSE) %>%
  select(Date = X1, Demand_Res = X2, Demand_Com = X4, Demand_Ind = X6) %>%
  mutate(Date = ymd(paste0(Date, "01")))

# 4. Merge weather and electricity demand data
final_data <- weather_data %>%
  inner_join(elec_demand, by = "Date")

knitr::opts_chunk$set(echo = TRUE)
```

## Step 1. Current Data Landscape: NC Energy Consumption & Sectoral Share

The primary goal of Step 1 is to establish a baseline profile of 
North Carolina’s energy demand. By disaggregating total consumption into 
Residential, Commercial, and Industrial sectors, we can identify which groups 
hold the largest stake in the state's energy portfolio and which exhibit the 
most significant volatility. This initial assessment provides the necessary 
context for our subsequent analysis of weather sensitivity, ultimately 
highlighting how increasing climate volatility and expanding temperature 
amplitudes are amplifying residential electricity peaks—a trend that poses 
growing risks to future grid reliability.


### 1-1. Visualization: Sectoral Electricity Consumption Patterns

This visualization illustrates the monthly electricity demand trends in North 
Carolina across the Residential, Commercial, and Industrial sectors from 2000 to 
2025. It serves as the empirical foundation for our hypothesis: that the 
residential sector is the most significant driver of the state's energy 
fluctuations.


```{r sectoral_demand_plot}

# 5. Visualization: Sectoral Electricity Demand

# Transform data to long format for plotting
demand_long <- final_data %>%
  select(Date, Demand_Res, Demand_Com, Demand_Ind) %>%
  pivot_longer(cols = starts_with("Demand"), 
               names_to = "Sector", 
               values_to = "Demand") %>%
  mutate(Sector = case_when(
    Sector == "Demand_Res" ~ "Residential",
    Sector == "Demand_Com" ~ "Commercial",
    Sector == "Demand_Ind" ~ "Industrial"
  ))

# Create the line plot to show volatility and base load
ggplot(demand_long, aes(x = Date, y = Demand, color = Sector)) +
  geom_line(linewidth = 0.8, alpha = 0.8) +
  # Manually set breaks starting from 2000
  scale_x_date(
    breaks = seq(as.Date("2000-01-01"), as.Date("2026-01-01"), by = "5 years"),
    date_labels = "%Y"
  ) + 
  labs(title = "Monthly Electricity Demand in North Carolina by Sector",
       subtitle = "Residential sector shows extreme volatility 
       compared to stable base loads",
       x = "Year",
       y = "Electricity Demand (Million kWh)",
       color = "Sector") +
  theme_minimal() +
  scale_color_manual(values = c("Residential" = "#0072B2", 
                                "Commercial" = "#D55E00", 
                                "Industrial" = "#009E73"))

```
Key Findings:

(1) Dominance and Seasonality of Residential Demand

The Residential sector (blue line) not only accounts for the highest overall 
consumption but also exhibits sharp, recurring "spikes" that dwarf the other 
sectors. The recurring double-peak pattern—peaking in both summer and 
winter—empirically confirms that residential demand is primarily driven by 
seasonal heating and cooling requirements.

(2) High Volatility vs. Stable Base Load

In contrast to the residential peaks, the Industrial (green) and Commercial 
(orange) sectors remain relatively flat and consistent over time. The 
Industrial sector, in particular, demonstrates a classic "Base Load" profile, 
where demand remains largely independent of outdoor temperature or seasonal 
transitions, reflecting constant operational needs.

(3) Expanding Variance and Peak Escalation

Over the 25-year period, there is a visible trend of increasing peak height in 
the residential sector. The distance between the troughs and the peaks appears 
to be widening, suggesting that North Carolina’s grid is facing growing pressure 
from extreme weather events and climate volatility.


### 1-2. Statistical Summary: Sectoral Share & Volatility

To provide a more rigorous basis for our observations, we calculated the average 
consumption share and the Coefficient of Variation (CV) for each sector. The CV 
is particularly important as it measures relative volatility, allowing us to 
compare the stability of sectors regardless of their total consumption volume.


```{r statistical summary}

# 6. Statistical Summary: Sectoral Share and Volatility (CV)

sector_stats <- demand_long %>%
  group_by(Sector) %>%
  summarise(
    Mean_Demand = mean(Demand),
    SD_Demand = sd(Demand),
    # Calculate Coefficient of Variation (CV) to compare relative volatility
    CV = (sd(Demand) / mean(Demand)) * 100
  ) %>%
  mutate(
    # Calculate overall share of each sector
    Total_Demand_Sum = sum(Mean_Demand),
    Share_Percentage = (Mean_Demand / Total_Demand_Sum) * 100
  ) %>%
  select(Sector, Mean_Demand, Share_Percentage, SD_Demand, CV) %>%
  arrange(desc(Share_Percentage))

# Display the summary table
print(sector_stats)

```

Key findings:

(1) The Largest Stakeholder

The residential sector accounts for the largest share of North Carolina’s 
electricity demand 43.46%, making its efficiency a top priority for state energy 
planning.

(2) Disproportionate Volatility

The CV of the Residential sector (21.5) is significantly higher than that of the 
Industrial(10.6) and Commercial(12.5) sectors. This statistically confirms that 
while industrial demand is predictable and stable, residential demand is the 
primary source of uncertainty and extreme fluctuations in the state's power 
grid.


## Step 2. Sensitivity Analysis 

In Step 1, we identified that North Carolina’s electricity landscape is 
characterized by a high reliance on the residential sector, which also exhibits 
the most extreme volatility. To ensure grid stability and design effective 
energy policies, it is crucial to move beyond identifying what is happening and 
investigate "why" these fluctuations occur.

While industrial and commercial sectors maintain a steady "Base Load" for 
operations, residential demand is heavily dictated by human comfort and 
behavioral responses to the environment. This sensitivity analysis aims to 
quantify the exact relationship between outdoor temperature and electricity 
consumption, providing a data-driven foundation for predicting peak demand. By 
measuring the "slope" of demand increase per degree of temperature change, we 
can identify the primary drivers of grid volatility and establish a clear 
mandate for targeted energy efficiency policies, such as residential insulation 
and smart load management, to enhance overall grid resilience.

In this section, we will employ both Scatter Plots (U-Curve) and Regression 
Analysis to examine the relationship between temperature and demand. By 
utilizing specialized metrics such as Heating Degree Days (HDD) and Cooling 
Degree Days (CDD), we will demonstrate that what appears to be random volatility 
is, in fact, a highly predictable response to North Carolina's climate patterns.


###2-1.Visualization: The Non-linear Relationship between Temperature and Demand

To empirically observe how temperature dictates energy consumption, we first 
visualize the relationship between the average monthly temperature and 
electricity demand across different sectors. This visual exploration is critical 
because energy demand does not follow a simple linear path; rather, it responds 
to the physical necessity of maintaining thermal comfort. 

```{r temp_demand_scatter}

# 7. Visualization: Temperature vs. Electricity Demand (U-Curve)

# Prepare data for scatter plot
scatter_data <- final_data %>%
  select(Date, AvgTemp, Demand_Res, Demand_Com, Demand_Ind) %>%
  pivot_longer(cols = starts_with("Demand"), 
               names_to = "Sector", 
               values_to = "Demand") %>%
  mutate(Sector = case_when(
    Sector == "Demand_Res" ~ "Residential",
    Sector == "Demand_Com" ~ "Commercial",
    Sector == "Demand_Ind" ~ "Industrial"
  ))

# Create the scatter plot with trend lines (LOESS)
ggplot(scatter_data, aes(x = AvgTemp, y = Demand, color = Sector)) +
  geom_point(alpha = 0.4) +
  # Add smooth trend lines to highlight the U-curve
  geom_smooth(method = "loess", se = FALSE, linewidth = 1.2) +
  labs(title = "Temperature vs. Electricity Demand by Sector",
       subtitle = "Residential sector exhibits a clear U-curve response to 
       temperature",
       x = "Average Temperature (°F)",
       y = "Electricity Demand (Million kWh)",
       color = "Sector") +
  theme_minimal() +
  scale_color_manual(values = c("Residential" = "#0072B2", 
                                "Commercial" = "#D55E00", 
                                "Industrial" = "#009E73"))


```

Key Findings:

(1) Distinct U-Curve for Residential Sector

The blue line (Residential) shows a clear U-shaped curve, indicating that 
electricity demand surges during both extreme cold (left) and extreme heat 
(right). This confirms that residential consumption is heavily driven by space 
heating and cooling needs. 

(2) Stable Base Load in Industrial & Commercial Sectors

In contrast, the Green (Industrial) and Orange (Commercial) lines are relatively 
flat, representing a "Base Load." Their electricity use remains consistent 
regardless of temperature changes, as industrial processes and office operations 
are less dependent on outdoor weather.

(3) The "Comfort Zone" or Balance Point

The lowest demand for all sectors occurs around 50°F to 70°F, where neither 
heating nor cooling is aggressively required.


### 2-2. Numerical Analysis: Quantifying the Sensitivity of Sectoral Demand

Following the visual confirmation of the "U-curve" relationship, this section 
provides a rigorous numerical assessment of how electricity demand reacts to 
temperature fluctuations. To achieve this, we utilize a "Balance Point" of 65°F
as the analytical threshold. In energy science, this standard assumes that at an 
outdoor temperature of 65°F, internal heat gains—produced by occupants, 
lighting, and appliances—are sufficient to maintain a comfortable indoor 
environment without the need for supplemental heating or cooling.

By bifurcating the data into Heating (<65°F) and Cooling (≥65°F) seasons, we can 
calculate the specific "Slope" (MWh/°F) for each sector. This allows us to 
quantify exactly how many units of electricity are consumed for every degree of 
deviation from the balance point, effectively identifying which sectors are the 
primary drivers of weather-induced load volatility.


```{r numerical analysis}

# 8. Numerical Analysis: Slopes for Heating and Cooling Seasons
# Setting the balance point at 65°F

# Categorize data into Heating (Temp < 65) and Cooling (Temp >= 65) seasons
seasonal_slopes <- final_data %>%
  pivot_longer(cols = c(Demand_Res, Demand_Com, Demand_Ind), 
               names_to = "Sector", values_to = "Demand") %>%
  mutate(Season = ifelse(AvgTemp < 65, "Heating_Season", "Cooling_Season"))

# Calculate slopes using linear regression for each sector and season
slope_results <- seasonal_slopes %>%
  group_by(Sector, Season) %>%
  do(model = lm(Demand ~ AvgTemp, data = .)) %>%
  summarise(
    Sector = Sector,
    Season = Season,
    # The 'Estimate' of AvgTemp is the slope
    Slope = coef(model)["AvgTemp"],
    # R-squared shows how well temperature explains the demand
    RSquared = summary(model)$r.squared
  ) %>%
  mutate(Sector = case_when(
    Sector == "Demand_Res" ~ "Residential",
    Sector == "Demand_Com" ~ "Commercial",
    Sector == "Demand_Ind" ~ "Industrial"
  )) %>%
  arrange(Sector, desc(Season))

# Display the results
print(slope_results)


```

Key Findings:

(1) Dominant Temperature Sensitivity in Residential Sector

The Residential sector shows the highest sensitivity to temperature. During the 
cooling season, for every 1°F increase in average temperature, residential 
electricity demand increases by approximately 191.6 million kWh. The high 
R-squared value (0.73) indicates that over 73% of the variation in residential 
demand can be explained by temperature alone, confirming it as the primary 
driver of consumption.

(2) Asymmetric Response: Cooling vs. Heating

The slope for the cooling season (191.64) is nearly double the magnitude of the 
heating season (-100.04). This suggests that in North Carolina, the reliance on 
electricity for air conditioning during summer is significantly more intense 
than the electricity used for heating in winter.

(3) Minimal Impact on Industrial & Commercial Sectors

In stark contrast, the Industrial sector shows a slope of only 6.23 during the 
cooling season with an R-squared near zero (0.01). This statistically proves 
that industrial demand is a "Base Load" that remains constant regardless of 
weather conditions. The Commercial sector shows some sensitivity during summer 
(Slope: 67.5) but is still only about one-third as sensitive as the residential 
sector.


### 2-3. Statistical Test for Slop Differences

To strictly verify whether the temperature sensitivity (slope) differs between 
sectors, a linear regression model with an interaction term (AvgTemp * Sector) 
was performed for the cooling season.

```{r statistical validation}

# 9. Statistical Test for Slope Differences using Interaction Terms

# We focus on the Cooling Season (Temp >= 65) as an example
cooling_data <- final_data %>%
  filter(AvgTemp >= 65) %>%
  pivot_longer(cols = c(Demand_Res, Demand_Com, Demand_Ind), 
               names_to = "Sector", values_to = "Demand")

# Fit a linear model with an interaction term: Demand ~ AvgTemp * Sector
# This tests if the effect of AvgTemp depends on the Sector
interaction_model <- lm(Demand ~ AvgTemp * Sector, data = cooling_data)

# Show the summary to see p-values for interaction terms
summary(interaction_model)

```

Key Findings:

(1) The interaction term AvgTem

SectorDemand_Res represents the difference in slopes between the Commercial 
(baseline) and Residential sectors. The positive coefficient (124.11) and the 
extremely low p-value (< 0.001) statistically prove that the Residential 
sector's demand increases significantly faster than other sectors as temperature 
rises.

(2) Robust Model Reliability

An R-squared value of 0.9268 indicates an exceptionally high model fit, 
confirming that the combination of temperature and sectoral characteristics 
almost perfectly predicts electricity demand patterns in North Carolina.


### 2-4. Correlation Analysis

While the previous regression analysis measured the "magnitude" of demand 
changes, the correlation analysis focuses on the "consistency" of the 
relationship. By utilizing Cooling Degree Days (CDD) and Heating Degree Days 
(HDD)—metrics specifically designed to reflect energy requirements—we can 
determine how much of the residential demand volatility is strictly governed by 
climate. This step is essential to confirm that the observed fluctuations are 
not random outliers but a highly synchronized response to North Carolina’s 
seasonal variations.

* CDD(Cooling Degree Days): A measure of how much the outdoor temperature stays 
above 65°F, representing the energy needed for air conditioning.
  HDD(Heating Degree Days): A measure of how much the outdoor temperature stays 
  below 65°F, representing the energy needed for heating.

```{r correlation_analysis}

# 10. correlation analysis

# Correlation during Cooling Season (Temp >= 65)
cooling_subset <- final_data %>% filter(AvgTemp >= 65)
cor_cooling <- cor(cooling_subset$Demand_Res, cooling_subset$CDD)

# Correlation during Heating Season (Temp < 65)
heating_subset <- final_data %>% filter(AvgTemp < 65)
cor_heating <- cor(heating_subset$Demand_Res, heating_subset$HDD)

# Print results
cat("Residential Correlation with CDD (Summer):", cor_cooling, "\n")
cat("Residential Correlation with HDD (Winter):", cor_heating, "\n")


```
Key Findings:

(1) High Degree of Synchronization

Both seasons exhibit correlation coefficients exceeding 0.83, which represents 
an extremely strong positive linear relationship. This indicates that as the 
thermal stress on a building increases, the electricity demand follows a nearly 
identical trajectory.

(2) Explanatory Power

By squaring these coefficients, we find that approximately 70% to 73% of the 
monthly variation in North Carolina’s residential electricity consumption is 
directly attributable to weather-driven heating and cooling needs.


## Step 3. Future Outlook & Trend Analysis: Climate Volatility and Peak Trends

Building upon the previous sectoral and sensitivity analyses, Step 3 shifts the 
focus toward the future outlook by examining the impact of climate volatility. 
As extreme weather events become more frequent, the "predictable" seasonal 
patterns are being replaced by high-amplitude temperature swings.

The analytical goal of this section is to investigate how these extreme 
temperature ranges (Max-Min differences) are directly amplifying electricity 
peaks in the residential sector. By analyzing the synchronization between 
temperature amplitude and peak demand, we aim to demonstrate that the challenges 
for North Carolina’s grid are not just about "average" demand, but about the 
widening variance and extreme outliers that threaten infrastructure capacity.


### 3-1. Time Series Analysis: Synchronization of Temperature Amplitude and Demand

To examine the immediate impact of climate volatility on the energy system, this 
section analyzes the synchronization between Temperature Amplitude 
(Max-Min Range) and residential electricity demand. Our initial objective was to 
observe whether the "spikiness" of weather fluctuations directly dictates the 
timing and magnitude of residential peaks. By overlaying these two variables, we
aim to visualize the direct coupling of environmental instability and grid 
stress.


```{r time series}

# 11. Time series analysis - synchoronization

step3_data <- final_data %>%
  mutate(Temp_Range = MaxTemp - MinTemp) %>% # Temperature Amplitude
  select(Date, Temp_Range, Demand_Res, AvgTemp)

# Note: Scaling is needed to overlay two different units on one plot
library(ggplot2)

split_scale <- 80 

ggplot(step3_data, aes(x = Date)) +
  # max-min temp
  geom_line(aes(y = Temp_Range * split_scale), 
            color = "gray85", size = 0.5, alpha = 0.7) +
  
  # residential elec demand
  geom_line(aes(y = Demand_Res), color = "#2c7fb8", size = 0.8) +
  
  # scale adjustment
  scale_y_continuous(
    name = "Residential Demand (MWh)",
    limits = c(0, 9000), 
    sec.axis = 
      sec_axis(~./split_scale, name = "Temperature Range (Max-Min, °F)")
  ) +
  labs(title = "Trend Analysis: Temperature Range vs. Residential Demand",
       subtitle = "Blue: Demand (Upper) | Gray: Temp Range (Lower)",
       x = "Year") +
  theme_minimal()


```
Key Findings:

The time-series visualization indicates that while the rhythm of electricity 
peaks is generally aligned with temperature swings, the visual evidence of 
"increasing volatility" is not immediately apparent. From a raw data 
perspective, the amplitude of temperature variations and the resulting demand 
spikes appear recurring but do not show a clear, observable expansion in 
variance over the 25-year period. This ambiguity necessitates a more rigorous 
statistical approach to isolate the underlying trends from seasonal noise.


### 3-2. STL Decomposition: Isolating the True Trend by Removing Seasonality

To gain a clearer understanding of the long-term trajectory, we applied STL 
Decomposition (Seasonal-Trend decomposition using LOESS) to both residential 
demand and temperature amplitude.

```{r STL decomposition - elec demand}

# 12. Eliminating seasonal effect (1) elec demand

Demand_ts <- ts(final_data$Demand_Res, start = c(2001, 1), frequency = 12)

Demand_decomp <- stl(Demand_ts, s.window = "periodic")

plot(Demand_decomp)

```
```{r STl decomposition - temp}

# 13. Eliminating seasonal effect (2) temp range

TempRange_ts <- ts(final_data$MaxTemp - final_data$MinTemp, start = c(2001, 1), 
                   frequency = 12)

TempRange_decomp <- stl(TempRange_ts, s.window = "periodic")

TempRange_deseasoned <- TempRange_ts - TempRange_decomp$time.series[, 1]

plot(TempRange_decomp)

```
Key Findings:

The decomposition results reveal a significant divergence between climate and 
energy.

(1) Temperature Amplitude

Contrary to our initial hypothesis that increasing climate volatility would be 
the primary driver of grid instability, the 25-year data shows that temperature 
variations in North Carolina have remained stable with no 
significant upward trend in amplitude.

(2) Residential Demand

Despite this climatic stability, residential electricity demand has exhibited 
expanding variance and escalating peaks.

(3) Hypothesis Reflection

These results partially contradict our initial hypothesis. While we expected 
"worsening weather" to be the driver, the data suggests that the structural 
growth in demand is occurring independently of climate volatility. This means 
that the growing vulnerability of the grid is not a "climate-side" escalation, 
but a "demand-side" intensification. The residential sector has become 
increasingly sensitive to existing weather patterns, meaning even "normal" 
weather swings now pose a greater threat to the infrastructure than they did two 
decades ago.


## Conclusion & Policy Implications

### Summary of Findings

This report investigated the factors threatening the resilience of North 
Carolina’s electricity grid through multiple analytical lenses:

Sectoral Dynamics: Analyses from Steps 1 and 2 confirmed that the Residential 
Sector, unlike the commercial or industrial sectors, is the primary driver of 
total grid peaks and is the most sensitive variable to temperature fluctuations.

The Volatility Paradox: STL Decomposition in Step 3 revealed that while 
temperature amplitude has remained stable since 2001, the intensity of 
residential demand peaks has escalated structurally. This suggests that shifting 
demographic patterns and residential environments have amplified "demand 
sensitivity" to existing weather conditions.


### Strategic Policy Recommendations

To address the demand-driven instability identified in this study, the following 
policies are recommended:

(1) Targeted Demand Response (DR)

Priority should be given to implementing variable pricing and incentive programs 
specifically for the residential sector, which shows the highest sensitivity to 
temperature swings.

(2) Residential Efficiency & Weatherization

Given that demand peaks are rising despite stable climate data, structural 
vulnerabilities such as poor insulation or inefficient HVAC systems in aging 
housing stocks may be at fault. Policy funding should be concentrated on 
weatherization programs for low-income and older residential areas to reduce 
systemic sensitivity.

(3) Resilient Infrastructure Planning

In spite of stable climate trends, "stress test" standards must be updated to 
reflect heightened demand elasticity. Conservative reserve margins and 
distribution grid upgrades in high-density residential areas are essential to 
accommodate the escalating peak intensity.


## Research Limitations & Future Tasks

(1) Temporal Resolution (Hourly vs. Monthly Data)

The primary limitation of this study is the reliance on monthly aggregated data. 
While effective for identifying long-term structural trends, monthly data masks 
the intra-day "Peak Intensity" and rapid demand fluctuations (Ramp Rates) that 
occur within a single hour.

(2) Geographic Scope

This analysis utilized state-level data for North Carolina, which does not 
account for the significant variance in electricity consumption patterns between 
high-density urban areas and rural residential zones.

(3) Behind-the-Meter (BTM) Factors

The study could not individually isolate the impacts of "Behind-the-Meter" 
factors, such as residential solar PV adoption or electric vehicle (EV) 
charging, which are increasingly critical drivers of modern residential demand 
volatility.





